\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-01 paper.qmd
Added main text for the data

>>>>

The S-curve model, denoted as $T$, is simulated through several steps. First, a random variable $x$ is generated from a uniform distribution between $-\frac{\pi}{2}$ and $\frac{\pi}{2}$, representing the parameter $x$ in the S-curve model. Next, three variables $x_1$, $x_2$, and $x_3$ are computed based on $x$ to construct the S-curve data. $x_1$ is calculated as the sine of $x$ (\@ref(eq:eqn2)), $x_2$ as twice the value of another uniformly distributed random variable between 0 and 1, and $x_3$ as the cosine of $x$ minus 1, multiplied by the sign of $x$. Additionally, four noise dimensions are introduced to the dataset to introduce variability: $x_4$, $x_5$, $x_6$, and $x_7$, each generated from uniform distributions within specific intervals. Finally, these variables are combined to form the S-curve dataset $T$.

\begin{equation} \label{eq-eqn1}
x_1 = \sin(3 \pi x)
\end{equation}

\begin{equation} \label{eq:eqn2}
x_2 = 2.0 \times U(0, 1)
\end{equation}

\begin{equation} \label{eq:eqn3}
x_3 = \text{sign}(x) \times (\cos(3 \pi x) - 1)
\end{equation}

\begin{equation} \label{eq:eqn4}
x_4, x_5 \sim U(-0.02, 0.02)
\end{equation}

\begin{equation} \label{eq:eqn5}
x_6 \sim U(-0.1, 0.1)
\end{equation}

\begin{equation} \label{eq:eqn6}
x_7 \sim U(-0.01, 0.01)
\end{equation}

### 2024-04-01 paper.tex
Added main text for the data

The S-curve model, denoted as ( T ), is simulated through a multi-step
process. Initially, a random variable ( T ) is generated from a uniform
distribution between (-\frac{\pi}{2}) and (\frac{\pi}{2}), representing
the parameter ( T ) in the S-curve model. Subsequently, three variables
( x\_1 ), ( x\_2 ), and ( x\_3 ) are computed based on ( T ) to
construct the S-curve data. ( x\_1 ) is calculated as the sine of ( T ),
( x\_2 ) as twice the value of another uniformly distributed random
variable between 0 and 1, and ( x\_3 ) as the cosine of ( T ) minus 1,
multiplied by the sign of ( T ). Additionally, four noise dimensions are
introduced to the dataset to introduce variability: ( x\_4 ), ( x\_5 ),
( x\_6 ), and ( x\_7 ), each generated from uniform distributions within
specific intervals. Finally, these variables are aggregated to form the
S-curve dataset ( X ).

Let ( T ) be a random variable uniformly distributed in the interval (
{[}-\frac{\pi}{2}, \frac{\pi}{2}{]} ), i.e., ( T
\sim U\left(-\frac{\pi}{2}, \frac{\pi}{2}\right) ).

Then, we define the following variables:

\begin{itemize}
\tightlist
\item
  ( x\_1 = \sin(3 \pi T) )
\item
  ( x\_2 = 2.0 \times U(0, 1) ), where ( U(0, 1) ) represents a uniform
  distribution between 0 and 1.
\item
  ( x\_3 = \text{sign}(T) \times (\cos(3 \pi T) - 1) )
\end{itemize}

Additionally, we introduce noise dimensions:

\begin{itemize}
\tightlist
\item
  ( x\_4, x\_5 ) are uniformly distributed random variables in the
  interval ( {[}-0.02, 0.02{]} ), i.e., ( x\_4, x\_5 \sim U(-0.02, 0.02)
  ).
\item
  ( x\_6 ) is a uniformly distributed random variable in the interval (
  {[}-0.1, 0.1{]} ), i.e., ( x\_6 \sim U(-0.1, 0.1) ).
\item
  ( x\_7 ) is a uniformly distributed random variable in the interval (
  {[}-0.01, 0.01{]} ), i.e., ( x\_7 \sim U(-0.01, 0.01) ).
\end{itemize}

Finally, we form the data matrix ( X ) by combining ( x\_1, x\_2, x\_3,
x\_4, x\_5, x\_6, ) and ( x\_7 ) into columns.

>>>>

The S-curve model, denoted as \(T\), is simulated through several steps.
First, a random variable \(x\) is generated from a uniform distribution
between \(-\frac{\pi}{2}\) and \(\frac{\pi}{2}\), representing the
parameter \(x\) in the S-curve model. Next, three variables \(x_1\),
\(x_2\), and \(x_3\) are computed based on \(x\) to construct the
S-curve data. \(x_1\) is calculated as the sine of \(x\)
(@ref(eq:eqn2)), \(x_2\) as twice the value of another uniformly
distributed random variable between 0 and 1, and \(x_3\) as the cosine
of \(x\) minus 1, multiplied by the sign of \(x\). Additionally, four
noise dimensions are introduced to the dataset to introduce variability:
\(x_4\), \(x_5\), \(x_6\), and \(x_7\), each generated from uniform
distributions within specific intervals. Finally, these variables are
combined to form the S-curve dataset \(T\).

\begin{equation} \label{eq-eqn1}
x_1 = \sin(3 \pi x)
\end{equation}

\begin{equation} \label{eq:eqn2}
x_2 = 2.0 \times U(0, 1)
\end{equation}

\begin{equation} \label{eq:eqn3}
x_3 = \text{sign}(x) \times (\cos(3 \pi x) - 1)
\end{equation}

\begin{equation} \label{eq:eqn4}
x_4, x_5 \sim U(-0.02, 0.02)
\end{equation}

\begin{equation} \label{eq:eqn5}
x_6 \sim U(-0.1, 0.1)
\end{equation}

\begin{equation} \label{eq:eqn6}
x_7 \sim U(-0.01, 0.01)
\end{equation}
